---
title: Investigating the exponential distribution and comparing it with the Central
  Limit Theorem
author: '@tribetect'
date: "August 18, 2015"
output: html_document
---

#Overview
In a few (2-3) sentences explain what is going to be reported on

We investigated the distribution of averages of 40 exponentials doing 1000 simulations.

#Simulations
 
 Include English explanations of the simulations you ran, with the accompanying R code. Your explanations should make clear what the R code accomplishes.
 
 
 
1. The exponential distribution was simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. 
2. Lambda was set = 0.2 for all of the simulations. 
3. Set number of simulations to 1000: variable, 'nosim'.


```{r}
hist(rexp(1000, .2))
```

and the distribution of 1000 averages of 40 random uniforms

```{r}
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(runif(40)))
hist(mns, main = "Distribution of 1000 means of sample size 40 from a uniformly distributed population")
```

# Sample Mean versus Theoretical Mean
Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers.

#Sample Variance versus Theoretical Variance
Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.

#Distribution
Via figures and text, explain how one can tell the distribution is approximately normal.

