---
title: 'Part 2: Analysis of Tooth Growth Data'
author: '@tribetect'
date: "August 15, 2015"
output: pdf_document
---

#Overview

#Exploratory data analysis

The data consists of 60 observations of growth, dose, and consists of two groups by growth supplement, 30 each of Orange Juice and 30 cases with 

```{r message=FALSE}
require(datasets); require(ggplot2)

qplot(len, data = ToothGrowth, facets = dose ~ supp, main = "Tooth growth", xlab = "Tooth length", ylab = "Observations")


```

## Summary of exploratory data analysis

### Comparative effectiveness of supplements
OJ may be more effective than VC, although the different may be very slight

### Effect of dose
Higher doses of supplement may result in more growth

#Hypothesis testing

### Null hypothesis: H0: mean_OJ = mean_VC 
Growth in teeth grouped by supplements OJ and VC is similar

###H_alt: Growth in teeth grouped by supplements OJ and VC is NOT 

```{r}
        t.test(len ~ supp, paired = FALSE, var.equal = TRUE, data = ToothGrowth)
```

## Assumptions
1. Length is predicted by dose and supp 
2. 95% confidence level is sufficient in reducing the likelyhood of inferential errors
3. Two groups of total 60 subjects are an unpaired groups
4. The variances of the two groups are assumed equal variance

## Conclusion
The two supplements, OJ and VC, do not differ significantly, we infer with 95% confidence. We do not reject our null hypothesis.